Hierarchical time series forecasting in Emergency Medical Services

### 2022-11-17 manuscript/06-conclusion.qmd
typo

Our results indicates that forecast reconciliation can not only contribute to a more coordinated efforts through producing coherent forecasts when it comes to using forecasting to inform decisions in EMS, but also it can result in forecast accuracy improvement. Our proposed forecasting models combined with reconciliation approaches outperform the empirical distribution benchmark. We show that a substantial forecast improvement can be achieved at higher levels of hierarchical and grouped structure time series by applying forecast reconciliation methods. When a point forecast is of interest at the bottom level of series, we observe that reconciliation may not improve the forecast accuracy, if the bottom series are noisy and lack systematic patterns. However, forecast reconciliation may result in more forecast results for bottom series, if we are interested in the tails of forecast distribution rather than just center measures like mean (i.e. point forecast). Producing consistent forecast are also crucial for informing planning activities, we also demonstrate that proposed models produce consistent forecasts across all forecast horizons. Therefore, we recommend that forecast recociliation approaches to be adopted for routine use in EMS, whenever hierarchical and/or grouped time series data need to be forecasted. Moreover, we found that using an ensemble forecasting model, combining al models developed in this paper, instead of using each individualy, works remarkably well for our mixed hierarchical & grouped stucture.

Further research could investigate the practical benefits of probabilistic hierarchical forecasting in EMS. Linking forecasts with its utilities (response time, resource utilisation, etc) can offer an opportunity to maximise benefits through more holistic planning approach. While, we generated count attend incident for the base forecast usign Poisson regression models, however the reconciles forecast is snot yet count. This could be also an avenue for further research.

>>>>

Our results indicates that forecast reconciliation can not only contribute to a more coordinated efforts through producing coherent forecasts when it comes to using forecasting to inform decisions in EMS, but also it can result in forecast accuracy improvement. Our proposed forecasting models combined with reconciliation approaches outperform the empirical distribution benchmark. We show that a substantial forecast improvement can be achieved at higher levels of hierarchical and grouped structure time series by applying forecast reconciliation methods. When a point forecast is of interest at the bottom level of series, we observe that reconciliation may not improve the forecast accuracy, if the bottom series are noisy and lack systematic patterns. However, forecast reconciliation may result in more forecast results for bottom series, if we are interested in the tails of forecast distribution rather than just center measures like mean (i.e. point forecast). Producing consistent forecast are also crucial for informing planning activities, we also demonstrate that proposed models produce consistent forecasts across all forecast horizons. Therefore, we recommend that forecast reconciliation approaches to be adopted for routine use in EMS, whenever hierarchical and/or grouped time series data need to be forecasted. Moreover, we found that using an ensemble forecasting model, combining all models developed in this paper, instead of using each individualy, works remarkably well for our mixed hierarchical & grouped structure.

Further research could investigate the practical benefits of probabilistic hierarchical forecasting in EMS. Linking forecasts with its utilities (response time, resource utilization, etc) can offer an opportunity to maximize benefits through more holistic planning approach. While, we generated count attend incident for the base forecast using Poisson regression models, however the reconciles forecast is snot yet count. This could be also an avenue for further research.
